weather_2

### 2021-09-01 Manuscript/Manuscript.Rmd
jhjh

The experiment was conducted in 2018 and 2019 under field conditions at five locations: Arlington, WI (43°18'N, 89°29'W), Clay Center, NE (40.57'N, 9814'W), Grant, NE (XXX'N, XXX'W), Lincoln, NE (41.16'N, 96.42'W), and Macomb, IL (XXX'N, XXX'W).

@@

The statistical analyses were performed using R statistical software version 4.0.1 [@rcoreteam2021]. Data analyses are stored at Zenodo [@oliveira2021b].

@@

>>>>

The experiment was conducted in 2018 and 2019 under field conditions at five locations: Arlington, WI (43°18'N, 89°29'W), Clay Center, NE (40.57'N, 9814'W), Grant, NE (40.85'N, -101.70'W), Lincoln, NE (41.16'N, 96.42'W), and Macomb, IL (XXX'N, XXX'W).

@@

The statistical analyses were performed using R statistical software version 4.0.1 [@rcoreteam2021].

@@

# Data accessibility {-}

The data and scripts used to analyse the data presented in this work can be found at Zenodo [@oliveira2021b].

### 2021-09-01 Manuscript/Manuscript.tex
jhjh

 & Hybrid & NK0142 3120-EZ1 & DKC60-67 &  &  & \\

 & Seeding rate & 88956 & 86487 &  &  & \\

 & Weed control & glyphosate / \emph{S}-metolachor & \emph{S}-metolachlor + trazine + mesotrione + bicyclopyrone\textsuperscript{d} &  &  & \\

 & Stage at 1\textsuperscript{st} cohort & V2-3 &  &  &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V6-7 &  &  &  & \\

 & Planting day & April 30, 2018 / May 5, 2019 & May 10, 2018/19 &  &  & \\

@@

 & Variety & DSR-1950 & AG21X8 &  &  & \\

 & Seeding rate & 296400 & 321237 &  &  & \\

 & Weed control & glyphosate / \emph{S}-metolachor & saflufenacil + imazethapyr + pyroxasulfone &  &  & \\

 & Stage at 1\textsuperscript{st} cohort & V1-2 &  &  &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V5-6 &  &  &  & \\

\multirow{-6}{*}{\raggedright\arraybackslash } & Planting day & May 5, 2018 / May 10, 2009 & May 14, 2018/19 &  &  & \\

>>>>

 & Hybrid & NK0142 3120-EZ1 & DKC60-67 & G03C84-5122-EZ1 &  & \\

 & Seeding rate & 88956 & 86487 & 79000 &  & \\

 & Weed control & glyphosate / \emph{S}-metolachor & \emph{S}-metolachlor + trazine + mesotrione + bicyclopyrone\textsuperscript{d} & glyphosate &  & \\

 & Stage at 1\textsuperscript{st} cohort & V2-3 &  & V2-3 &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V6-7 &  & V6-7 &  & \\

 & Planting day & April 30, 2018 / May 5, 2019 & May 10, 2018/19 &  May 5, 2018 / May 14, 2019 &  & \\

@@

 & Variety & DSR-1950 & AG21X8 & AG28X7 &  & \\

 & Seeding rate & 296400 & 321237 & 220000 &  & \\

 & Weed control & glyphosate / \emph{S}-metolachor & saflufenacil + imazethapyr + pyroxasulfone &  glyphosate &  & \\

 & Stage at 1\textsuperscript{st} cohort & V1-2 &  & V1-2 &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V5-6 &  & V5-6 &  & \\

\multirow{-6}{*}{\raggedright\arraybackslash } & Planting day & May 5, 2018 / May 10, 2009 & May 14, 2018/19 & May 15, 2018 / May 3, 2019 &  & \\

### 2021-09-01 data analysis/weather/weather_2.Rmd
jhjh

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  mutate(site = fct_recode(site, 
                           "Arlington, WI" = "Arlington",
                           "Clay Center, NE" = "Clay Center",
                           "Grant, NE" = "Grant",
                           "Lincoln, NE" = "Lincoln",
                           "Macomb, IL" = "Macomb")) -> adaptation_pp
```

>>>>

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
#  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  mutate(site = fct_recode(site, 
                           "Arlington, WI" = "Arlington",
                           "Clay Center, NE" = "Clay Center",
                           "Grant, NE" = "Grant",
                           "Lincoln, NE" = "Lincoln",
                           "Macomb, IL" = "Macomb")) -> adaptation_pp
```

```{r}
adaptation_pp %>% 
  filter(!year %in% c(2018, 2019)) %>% 
ggplot(aes(x = month_lab, y = pp)) +
  stat_eye(position = "dodge")
```
